\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Propuesta Individual}

### 2016-02-24 article.tex
Added images to tex file

\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage{varwidth}
\usepackage{hyperref}

@@

@@

%----------------------------------------------------------------------------------------
%	Bibliographic references
%----------------------------------------------------------------------------------------
	\begin{thebibliography}{9}

>>>>

\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage{varwidth}
\usepackage{hyperref}
\usepackage{graphicx}

@@

			\paragraph{}
			Página Web
			\begin{figure}[H]
				\centering
				\begin{minipage}[b]{0.7\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_login.png}
				\end{minipage}
			\end{figure}

@@

			\begin{figure}[H]
				\centering
				\begin{minipage}[b]{0.49\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_create_account.png}
				\end{minipage}
				\begin{minipage}[b]{0.49\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_create_account_carrier.png}
				\end{minipage}
			\end{figure}

			\begin{figure}[H]
				\centering
				\begin{minipage}[b]{0.49\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_home.png}

				\end{minipage}
				\begin{minipage}[b]{0.49\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_home_carrier.png}

				\end{minipage}
			\end{figure}

			\begin{figure}[H]
				\centering
				\begin{minipage}[b]{0.49\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_deliveries.png}

				\end{minipage}
				\begin{minipage}[b]{0.49\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_deliveries_carrier.png}

				\end{minipage}
			\end{figure}

			\begin{figure}[H]
				\centering
				\begin{minipage}[b]{0.49\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_stats.png}

				\end{minipage}
				\begin{minipage}[b]{0.49\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_stats_carrier.png}

				\end{minipage}
			\end{figure}

			\begin{figure}[H]
				\centering
				\begin{minipage}[b]{0.7\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_create_delivery.png}

				\end{minipage}
			\end{figure}

			\begin{figure}[H]
				\centering
				\begin{minipage}[b]{0.7\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_search_deliveries.png}

				\end{minipage}
			\end{figure}

			\begin{figure}[H]
				\centering
				\begin{minipage}[b]{0.7\textwidth}
					\includegraphics[width=\textwidth]{res/sketch_delivery.png}

				\end{minipage}
			\end{figure}

			\paragraph{}
			Página Web
%----------------------------------------------------------------------------------------
%	Bibliographic references
%----------------------------------------------------------------------------------------
	\begin{thebibliography}{9}
